---
title: "Memory in Action 3: Semantic memory"
output: 
  html_document:
    toc: true
date: "2023-04-13"
---

```{r setup, echo=F}
knitr::opts_chunk$set(echo = TRUE, warning=F, message=F)
library(tidyverse)
library(here)
library(ggthemes)
theme_set(theme_bw())
knitr::opts_chunk$set(dev = "png", dev.args = list(type = "cairo-png"))

images <- "images_3"
```

```{r, echo=F}
library(googledrive)


f <- googledrive::as_dribble("https://docs.google.com/spreadsheets/d/1mcsrBWIXBK5yMrgpuCxQLoFbLnW8L-Qi9DFkI6bmdgE/edit#gid=332008038")
googledrive::drive_download(f, path=here("data_3","semantic.xlsx"), overwrite=T)


semantic <- readxl::read_xlsx(here("data_3","semantic.xlsx"), 
                       sheet="Form Responses 1", skip=0) 

```

These visualizations are based on `r nrow(semantic)` submissions. 

```{r}

dat <- semantic |> select(-Timestamp, -`Email Address`, -Name, -`SUNet ID`) |> 
  pivot_longer(everything()) |> separate(name, c("type", "instance")) 



ggplot(dat, aes(x=reorder(instance, value), y=value, color=type))+
  geom_jitter(, height=.1, width=.2, alpha=.1)+
  stat_summary(fun.data = "mean_cl_boot", color="black")+
  facet_wrap(~type, scales="free_x")+
  theme(legend.position = "none")+
  labs(y="Goodness as example of class", x="")

         
    

ggsave(here(images, "dist.png"), dev="png")

```
There looks to be a correlation between the average ratings and the spread of the ratings. The prototypical examples like apple get almost uniformly rated as a 1 ("good example of the class") whereas less prototypical examples have less agreement -- some people think wresting is a good example of a sport, but others don't. 

Might be something to do with how people are using the scales? Like, maybe some people are thinking "well, an ostrich isn't that great of a bird, but at least it's still a bird" and would only use 6 or 7 on the scale for say lizard (it's such a bad example of a bird, it's not even a bird). I'm surprised by the ostrich / wren ordering. 
